---
title: "Workers' Compensation"
author: "Molly Hischke & Kyle Hancock"
date: "3/13/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Introduction (4 pts - Kyle)

- Background
- Identify research question(s)
- State response and predictor variables
- Identify each variable as continuous or categorical (with levels)
- Identify observational/experimental units and number of observations
- Further details of design


# Summary statistics and/or graphics (4 pts - Kyle)

```{r Load & Clean Data, warning=FALSE, message=FALSE}
library(readr)
library(tidyr)
library(dplyr)
library(ggplot2)
library(car)
library(emmeans)
wc <- read_csv("../data/craftbeer_wc.csv")

wc2 <- wc %>% 
  group_by(Policy_Dim_Key, year) %>% 
  summarize(avg_payroll = mean(adj_payroll),
            total_claims = sum(Claim_Count)) %>% 
  mutate(claim_filed = ifelse(total_claims == 0, 0, 1)) %>% 
  ungroup() %>% 
  mutate(Policy_Dim_Key = as.factor(Policy_Dim_Key),
         year = as.factor(year))
```

```{r Summary Statistics & Graphics}

```

# Analysis (6 pts - Molly)

```{r Binary Response with Repeated Measures}
library(geepack)
Model2 <- geeglm(claim_filed ~ adj_payroll, id = Policy_Dim_Key,
                         family = binomial(link = "logit"), 
                         corstr = "exchangeable", data = wc)
summary(Model2)
```


```{r Count Response with Repeated Measures}
library(geepack)
Model4 <- geeglm(claim_filed ~ adj_payroll, id = Policy_Dim_Key,
                         family = poisson(link = "log"), 
                         corstr = "exchangeable", data = wc)
summary(Model4)


```

# Results and Conclusions (4 pts - Molly)

- ANOVA style likelihood ratio tests and/or table of estimated coefficients
- Other results as appropriate (ex: pairwise comparisons for categorical predictor)
- Interpretation and discussion (even if nothing is "significant")
- Respond to your research questions

# R code appendix

Add the code chunk from the HW assignments. 





